---
title: "Paired T-Test"
output:
  html_document:
    toc_float: false
    includes:
      before_body: [include_tlm_nav.html]
      after_body: [include_tlm_nav_end.html, footer.html]
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message=FALSE, warning=FALSE, echo = FALSE}
# packages
library(xxxxx) # xxxxxx
library(xxxxx) # xxxxxx
```

```{r, echo = FALSE}
# Load the data:
mydata <- read_sav("/path-to-data")
```

## x.1: Paired T-Test

This is an example xxxxxxx

### Overview of Model
xxxxxxx

### Diagram
```{r xxxxx_graph, echo=FALSE}
grViz('/path-to-diagram', width='100%', height='25%')
fig.cap = "insert figure caption"
```

### Explanation of Model Code
```{r Example_x.1, eval=FALSE, class.source = 'fold-show'}
model xxxxx
```
  3a. List of model parameters
  3b. Line-by-Line Code Breakdown
    3b1. Insert code snippet 1
    3b2. Description of code snippet 1
    3b3. Insert additional code snippets as necessary
    3b4. Description of additional code snippets
   
4. Model Code- ABCD Data Example
  4a. Model Code 
  4b. Output
  4b. Results write-up
  4c. Plots
  4d. Tables

***
## [Continue to Univariate Repeated-Measures ANOVA](tlm-6.html){.continue-link}
