---
title: "Simple Descriptive and Group Means"
output:
  html_document:
    toc_float: false
    includes:
      before_body: [include_tlm_nav.html]
      after_body: [include_tlm_nav_end.html, footer.html]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message=FALSE, warning=FALSE, echo = FALSE}
# packages
library(xxxxx) # xxxxxx
library(xxxxx) # xxxxxx
```

```{r, echo = FALSE}
# Load the data:
mydata <- read_sav("/path-to-data")
```

1. Example Title
  1a. concise description of example

2. Overview of Model

3. Model Code- Generic Example (using non-specific variables [e.g., x, y, t1, t2])
  3a. List of model parameters
  3b. Line-by-Line Code Breakdown
    3b1. Insert code snippet 1
    3b2. Description of code snippet 1
    3b3. Insert additional code snippets as necessary
    3b4. Description of additional code snippets
   
4. Model Code- ABCD Data Example
  4a. Model Code 
  4b. Output
  4b. Results write-up
  4c. Plots
  4d. Tables
***
## [Continue to Change Scores](tlm-3.html){.continue-link}
